---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
data <- read.csv("./data/activity.csv", na.string="NA")
```

## What is mean total number of steps taken per day?
The total number of steps taken per day:
```{r}
calc <- tapply(data$steps, data$date, FUN=sum, na.rm=TRUE)
nrow(calc)
```

Histogram of the total number of steps taken each day:
```{r}
hist(calc, main="The total number of steps taken each day", breaks=20, col="red")
```

The mean of the total number of steps taken per day:
```{r}
mean(calc, na.rm=TRUE)
```
The median of the total number of steps taken per day:
```{r}
median(calc, na.rm=TRUE)
```

## What is the average daily activity pattern?
```{r}
library(ggplot2) 
averages <- aggregate(x=list(steps=data$steps), by=list(interval=data$interval), FUN=mean, na.rm=TRUE) 
ggplot(data=averages, aes(x=interval, y=steps)) + geom_line() + xlab("interval") + ylab("average")
max(data$steps, na.rm=TRUE)
```

## Imputing missing values
```{r}
all <- nrow(data)
steps <- na.omit(data)
not_na <- nrow(steps)
```

Missing value
```{r}
all-not_na
```

Create new dataset replace missing value by 100
```{r}
copy_data <- data
copy_data$steps[is.na(copy_data$steps)] <- 100
```

Histogram of new dataset
```{r}
new_calc <- tapply(copy_data$steps, copy_data$date, FUN=sum)
hist(new_calc, main="The total number of steps taken each day", breaks=20, col="red")
```

The mean of the total number of steps taken per day (new dataset):
```{r}
mean(new_calc)
```

The median of the total number of steps taken per day (new dataset):
```{r}
median(new_calc)
```

## Are there differences in activity patterns between weekdays and weekends?
Filter data following weekday and weekend:
```{r}
is_weekend <- function(date) {
  if(weekdays(as.Date(date)) %in% c("Saturday", "Sunday"))
     return ("WEEKEND")
  else
     return ("WEEKDAY")
}
data$day <- sapply(data$date, FUN=is_weekend)
```
Plot:
```{r}
averages <- aggregate(steps ~ interval + day, data=data, mean) 
ggplot(averages, aes(interval, steps)) + geom_line() + facet_grid(day ~ .) + 
   xlab("5-minute interval") + ylab("Number of steps")
```
